---
title: "Clean"
output: html_document
---

Set the work directory according to where the folder is on your computer.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, root.dir = 'D:/Google Drive/MatOk/P6 (Bachelor)/P6Kode')
```

```{r}
library(readxl)
library(readr)
library(tidyverse) 
library(plyr)
library(data.table)
library(zoo)
```

Start by importing data. (Put the price and consumption into 2 different folders, input those locations of the data in line 24 and 35)
```{r, echo=FALSE}
my_read_excel <- function(x) {read_xlsx(path = x, range = "A3:D368", na = "")}
my_read_excel2 <- function(x) {read_xlsx(path = x, range = "A3:D143", na = "")}
setwd("D:/Google Drive/MatOk/R/P6Kode/Data/Daily/Consumption")
getwd()
consum_files <- list.files();consum_files
con_data <- my_read_excel(consum_files[1])
con_data <- rbind(con_data, read_xlsx(path = consum_files[2], range = "A3:D369", na = "")) #Add additional day for leap year
con_data <- rbind(con_data, ldply(consum_files[3:5], my_read_excel))
con_data <- rbind(con_data, ldply(consum_files[6], my_read_excel2))


my_read_excel <- function(x) {read_xlsx(path = x, range = "A3:I368", na = "")}
my_read_excel2 <- function(x) {read_xlsx(path = x, range = "A3:I143", na = "")}
setwd("D:/Google Drive/MatOk/R/P6Kode/Data/Daily/Prices")
getwd()
price_files <- list.files();price_files
price_data <- my_read_excel(price_files[1])
price_data <- rbind(price_data, read_xlsx(path = price_files[2], range = "A3:I369", na = "")) #Add additional day for leap year
price_data <- rbind(price_data, ldply(price_files[3:5], my_read_excel))
price_data <- rbind(price_data, ldply(price_files[6], my_read_excel2))
price_data <- price_data[,c(1,8,9)]

#tmp1 <- as.numeric(sub(",",".", as.matrix(price_data[,3:4])[,1]))
#tmp2 <- as.numeric(sub(",",".", as.matrix(price_data[,3:4])[,2]))
#price_data[,3:4] <- cbind(tmp1,tmp2)
```

Fix several observations for the same point in time.
```{r}
tmp_con_data <- as.data.table(con_data)
tmp_price_data <- as.data.table(price_data)
keys <- c("...1")

#Clean Consumption
keys <- c("...1")
tmp_con_data <- tmp_con_data[,list(DK1 = mean(DK1), DK2 = mean(DK2), DK = mean(DK)), keys]

#Clean Price
keys <- c("...1")
tmp_price_data <- tmp_price_data[,list(DK1 = mean(DK1), DK2 = mean(DK2)), keys]
```


Interpolation by linear approximation
```{r}
#Consumption
DK1 <- na.approx(tmp_con_data[,2])
DK2 <- na.approx(tmp_con_data[,3])
DK <- na.approx(tmp_con_data[,4])
tmp_con_data <- cbind(tmp_con_data[,1],DK1,DK2,DK)

#Price
DK1 <- na.approx(tmp_price_data[,2])
DK2 <- na.approx(tmp_price_data[,3])
tmp_price_data <- cbind(tmp_price_data[,1],DK1,DK2)
```


Fix time/date column (Make it a better format)
```{r}
clean_con_data <- as_tibble(tmp_con_data)
clean_price_data <- as_tibble(tmp_price_data)

time_vector <- seq(ISOdate(2015,1,1,13), ISOdate(2019,12,31,13), "days")

clean_price_data <- cbind(time_vector ,clean_price_data[,2:3])
colnames(clean_price_data)[1] <- "Time"

clean_con_data <- cbind(time_vector ,clean_con_data[,2:4])
colnames(clean_con_data)[1] <- "Time"
```


Final touch
```{r}
clean_price_data <- cbind(clean_price_data[,1:3], (clean_price_data[,2]+clean_price_data[,3])/2)
colnames(clean_price_data)[4] <- "DK"

View(clean_con_data);View(clean_price_data)

all_data <- list(clean_price_data, clean_con_data)
names(all_data) <- c("Price","Consumption")

tc <- seq(1, length(clean_con_data$DK1))
plot(clean_con_data$Time, clean_con_data$DK1, xlab = "Time", ylab = "Consumption", type ="l")
```

Gem det ffrdige data
```{r}
rm(list=setdiff(ls(), c("all_data", "clean_con_data", "clean_price_data")))
```








Experimental Section (Trash can)
```{r}
dup_fiks <- function( DATA, r1 = c(1:2), r2 = m_rows )
{
  dups <- which(duplicated(DATA[,r1]) == TRUE)
  n <- length(dups)
  mean_val <- matrix(rep(0,n*length(m_rows)), nrow = n)
  print(mean_val)
  new_DATA <- DATA
  for (i in 1:n) {
    mean_val[i,] <- as.numeric((DATA[dups[i], m_rows] + DATA[dups[i]-1, m_rows])/2)
    print(mean_val[i,])
    new_DATA[dups[i]-1,m_rows] <- mean_val[i,]
  }
  new_DATA <- new_DATA[-dups]
}
m_rows <- c(3:5)
dup_fiks(con_data)
```


Cleanup
```{r}
which(duplicated(price_data[,1:2]) == TRUE)
#Fiks duplikater (Virker for 2 observationer op ad hinanden)
clean_con_data <- con_data %>% group_by(...1,Hours) %>% summarise_all(funs(mean))


clean_price_data <- price_data %>% group_by(...1,Hours) %>% summarise_all(funs(mean))



```

test2
```{r}
library(data.table)
dat <- read.table(text='name    value   etc1    etc2
A       9       1       X
A       10      1       X
A       11      1       X
B       2       1       Y
C       40      1       Y
C       50      1       Y',header=TRUE)
keys <- colnames(dat)[!grepl('value',colnames(dat))]
X <- as.data.table(dat)
X[,list(mm= mean(value)),keys]
X[,list(mm= mean(value)),keys]
```

