---
title: "SVARmodellering"
author: "Jens Kramer Rold Jensen"
date: "2020 M05 15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(vars)
library(svars)
library(aTSA)
library(graphics)
library(dse)
library(astsa)
library(corrplot)
```


Load functions and data.
```{r}
getwd()
setwd("D:/Google Drive/MatOk/R/P6Kode")#Jens pc
#setwd("C:/Users/laust/Desktop/P6Kode")#Laust pc
source("Kode/Funktioner.R")
load("Data/Daily/StationaryTS/stationaryTS(Final3).RData")
load("Data/Daily/Clean/all_data(2020).RData")
```

Define data
```{r}
C <- data.Decomposition$Consumption[,4]; C <- C[-c(1:100)]
P <- data.Decomposition$Price[,4]; P <- P[-c(1:100)]
dataM <- cbind(C,P)
```

Test for stationarity (Augmented Dickey Fuller)
```{r}
a <- adf.test(C, nlag = 50, output = FALSE)
which(a$type1[,3] >= 0.05) #Which p-values are above 0.05? (large p-value = non-stationary)
b <- adf.test(P, nlag = 50, output = FALSE)
which(b$type1[,3] >= 0.05) #Which p-values are above 0.05? (large p-value = non-stationary)
```

VAR model
```{r}
info <- VARselect(dataM, lag.max = 50) #Best VAR model based on information criteria
best.f <- function(x) {
  which(x == min(x))
}
apply(info$criteria, 1, best.f) #BIC/SC says a model with 4 is best.
VAR.model <- VAR(dataM, p = 9) #Estimates the model using OLS on the companion form.
#VAR.model <- restrict(VAR.model, method = "ser")
sum_VAR <- summary(VAR.model)
summary(VAR.model$varresult$C)$coefficients
```

Plot residuals and the ACF
```{r}
time <- all_data$Price$Time[-c(1:249)]
#Consumption
plot(time, VAR.model$varresult$C$residuals, type = "l")
acf2(VAR.model$varresult$C$residuals, max.lag = 500)

#Price
plot(time, VAR.model$varresult$P$residuals, type = "l")
acf2(VAR.model$varresult$P$residuals, max.lag = 500)
```

Summary of VAR variables
```{r}
VAR_Consumption_summary <- summary(VAR.model$varresult$C)
VAR_Price_summary <- summary(VAR.model$varresult$P)

```


Identification of the contemporal parameter on the error term by cholesky decomposition (B)
```{r}
C_residuals <- VAR.model$varresult$C$residuals
P_residuals <- VAR.model$varresult$P$residuals
covM_residuals <- cov(cbind(C_residuals, P_residuals))
corM_residuals <- cor(cbind(C_residuals, P_residuals))
Bman <- t(chol(covM_residuals))
Bman <- cbind(Bman[,1]/Bman[1,1],Bman[,2]/Bman[2,2])
Bman
```

SVAR model (B)
```{r}
bmat <- diag(2)
bmat[2,1] <- NA
SVARB.model <- SVAR(VAR.model, estmethod = "direct", Bmat = bmat, max.iter = 1000) #Uses ML-estimation 
```

IRF's for the SVAR B-model
```{r}
SVMA_coef <- Phi(SVARB.model)
m <- dim(SVMA_coef)[3]
Theta <- vector(mode = "list", m)
for (i in 1:m) {
  Theta[[i]] <- SVMA_coef[,,i]
}
```

Tests 
```{r}
A <- SVARB.model$A
B <- SVARB.model$B
inv_QR(SVARB.model$B) %*% c(C_residuals[1], P_residuals[1])
inv_QR(A) %*% B 
A %*% B%*% t(B) %*% t(A) #It almost gives the cov matrix of the residuals of the VAR model
```

IRA (Impulse Response Analysis)
```{r}
####SVAR
###Make the IRF
irf_SVARB <- irf(SVARB.model, runs = 100)
irf_SVARB <- irf(SVARB.model, runs = 100, ortho = TRUE)


layout(matrix(c(1,2,3,4),2,2,  byrow = TRUE))
###Consumption Impulse/Price Response
##Consumption
#IRF and confidence interval assimilation
conf_upper <- irf_SVARB$Upper$C[,1]
conf_lower <- irf_SVARB$Lower$C[,1]
m <- length(irf_SVARB$Lower$C[,1])


#Plot
#text("Test")
plot(1:m,irf_SVARB$irf$C[,1], ylim = c(min(conf_lower), max(conf_upper)), type = "l", xlab="Time", ylab= "Consumption", font.main=1, main="Consumption")
lines(1:m, conf_upper, col = "red", lty = "dashed")
lines(1:m, conf_lower, col = "red", lty = "dashed")
lines(1:m, rep(0,m), col = "blue")

##Price
#IRF and confidence interval assimilation
conf_upper <- irf_SVARB$Upper$C[,2]
conf_lower <- irf_SVARB$Lower$C[,2]
m <- length(irf_SVARB$Lower$C[,2])

#Plot
plot(1:m,irf_SVARB$irf$C[,2], ylim = c(min(conf_lower), max(conf_upper)), type = "l", xlab="Time", ylab= "", font.main=1, main="Price")
lines(1:m, conf_upper, col = "red", lty = "dashed")
lines(1:m, conf_lower, col = "red", lty = "dashed")
lines(1:m, rep(0,m), col = "blue", lty = "dotted")

###Price Impulse/Consumption Response
##Consumption
#IRF and confidence interval assimilation
conf_upper <- irf_SVARB$Upper$P[,1]
conf_lower <- irf_SVARB$Lower$P[,1]
m <- length(irf_SVARB$Lower$P[,1])

#Plot
plot(1:m,irf_SVARB$irf$P[,1], ylim = c(min(conf_lower), max(conf_upper)), type = "l", xlab="Time", ylab= "Price")
lines(1:m, conf_upper, col = "red", lty = "dashed")
lines(1:m, conf_lower, col = "red", lty = "dashed")
lines(1:m, rep(0,m), col = "blue", lty = "dotted")

##Price
#IRF and confidence interval assimilation
conf_upper <- irf_SVARB$Upper$P[,2]
conf_lower <- irf_SVARB$Lower$P[,2]
m <- length(irf_SVARB$Lower$P[,2])

#Plot
plot(1:m,irf_SVARB$irf$P[,2], ylim = c(min(conf_lower), max(conf_upper)), type = "l", xlab="Time", ylab= "")
lines(1:m, conf_upper, col = "red", lty = "dashed")
lines(1:m, conf_lower, col = "red", lty = "dashed")
lines(1:m, rep(0,m), col = "blue", lty = "dotted")
```

Forecasting (Without DC)
```{r}
m <- 10 
forecast.SVARB <- predict(VAR.model, n.ahead = (m))

layout( matrix(c(1,2),2,1,byrow = TRUE) )
##Consumption
finalC <- C[length(C)]
fcst_SVARB <- forecast.SVARB$fcst$C[,1]
conf_upper <- forecast.SVARB$fcst$C[,3]
conf_lower <- forecast.SVARB$fcst$C[,2]
#Plots
plot(1:m, c(fcst_SVARB), ylim = c(min(conf_lower), max(conf_upper)), type = "l", ylab= "")
lines(1:m, conf_upper, col = "red", lty = "dashed")
lines(1:m, conf_lower, col = "red", lty = "dashed")
lines(1:m, rep(0,m), col = "blue", lty = "dotted")
#lines(conf_lower[1],conf_upper[1], col = "red")
#lines(c(2,2) , c(conf_upper[1], conf_lower[1]), col = "red", lty = "dashed")


##Price
finalP <- P[length(P)]
fcst_SVARB <- forecast.SVARB$fcst$P[,1]
conf_upper <- forecast.SVARB$fcst$P[,3]
conf_lower <- forecast.SVARB$fcst$P[,2]
#Plots
plot(1:m, c(fcst_SVARB), ylim = c(min(conf_lower), max(conf_upper)), type = "l", ylab= "")
lines(1:m, conf_upper, col = "red", lty = "dashed")
lines(1:m, conf_lower, col = "red", lty = "dashed")
lines(1:m, rep(0,m), col = "blue", lty = "dotted")
#lines(c(2,2) , c(conf_upper[1], conf_lower[1]), col = "red", lty = "dashed")

```

Forecasting (With DC)
```{r}
m <- 30 
i <- 0
forecast.SVARB <- predict(VAR.model, n.ahead = m)
Time <- all_data$Consumption$Time
timeframe <- seq(as.Date("22/11/2019", format = "%d/%m/%Y"),
             by = "days", length = 40)
tfxlim <- c(as.Date("22/11/2019", format = "%d/%m/%Y"), as.Date("30/01/2020", format = "%d/%m/%Y"))
e1 <- timeframe[length(timeframe)] + 1

#layout(matrix(c(1,2),2,1,byrow = TRUE))
###Consumption
##Forecast
C_fcst_SVARB <- forecast.SVARB$fcst$C[,1]
C_conf_upper <- forecast.SVARB$fcst$C[,3]
C_conf_lower <- forecast.SVARB$fcst$C[,2]
##Adding the DC components and seasonal parts!
#Defining polynomial, added deterministic components etc.
DC10_C <- data.Decomposition$Consumption[1:30, 6]
C_Poly <- data.Decomposition$Consumption[1:8, 5]
C_orig <- data.Decomposition$Consumption[-c(1:100),1]
C_actual <- all_data$Consumption$DK2[(1827:1926)-i]


C_fcst <- polyinvers(c(C[(1717:1726)-i],forecast.SVARB$fcst$C[,1]), C_Poly, 10)[-c(1:10)] + DC10_C
C_CI_upper <- polyinvers(c(C[(1717:1726)-i],forecast.SVARB$fcst$C[,3]), C_Poly, 10)[-c(1:10)] + DC10_C
C_CI_lower <- polyinvers(c(C[(1717:1726)-i],forecast.SVARB$fcst$C[,2]), C_Poly, 10)[-c(1:10)] + DC10_C

#Plots
plot(timeframe, 
     c(C_orig[1687:1726]), 
     xlim = tfxlim, 
     ylim = c(min(c(C_orig[(1637:1726)-i],C_CI_lower)), max(c(C_orig[(1687:1726)-i],C_CI_upper))), 
     type = "l", 
     ylab= "kWh", 
     xlab = "",
     main = "Consumption Forecast Winter 2019-2020"
     )
legend(timeframe[1]-2.75,46130,
       c("Real Cons.","CI","Forecast"), 
       lwd=c(1,1,1), 
       col=c("black","red","black"), 
       lty = c("solid","dashed","dotted"), 
       y.intersp= .79
       )
lines(c((e1-1):(e1+29)), c(C_orig[1726-i],C_fcst), lty = "dotted")
lines(c((e1):(e1+29)), C_CI_lower, col = "red", lty = "dashed")
lines(c((e1):(e1+29)), C_CI_upper, col = "red", lty = "dashed")
lines(c((e1-1):(e1)), c(C_orig[1726-i], C_CI_upper[1]), lty = "dashed", col = "red")
lines(c((e1-1):(e1)), c(C_orig[1726-i], C_CI_lower[1]), lty = "dashed", col = "red")

#lines(timeframe, rep(0,40), col = "blue", lty = "dotted")

points(c((e1-1):(e1+29)), c(C_orig[1726], C_actual[1:30]))
lines(c((e1-1):(e1+29)), c(C_orig[1726], C_actual[1:30]))

###Price
##Forecast
P_fcst_SVARB <- forecast.SVARB$fcst$P[,1]
P_conf_upper <- forecast.SVARB$fcst$P[,3]
P_conf_lower <- forecast.SVARB$fcst$P[,2]
##Adding the DC components and seasonal parts!
#Defining polynomial, added deterministic components etc.
DC10_P <- data.Decomposition$Price[1:30, 6]
P_Poly <- data.Decomposition$Price[1:8, 5]
P_orig <- data.Decomposition$Price[-c(1:100),1]
P_actual <- all_data$Price$DK2[1827:1926]

P_fcst <- polymult(c(P[1717:1726],forecast.SVARB$fcst$P[,1]), P_Poly, 1)[-c(1:10)] + DC10_P 
P_CI_upper <- polymult(c(P_orig[1717:1726],forecast.SVARB$fcst$P[,3]), P_Poly, 1)[-c(1:10)] + DC10_P 
P_CI_lower <- polymult(c(P[1717:1726],forecast.SVARB$fcst$P[,2]), P_Poly, 1)[-c(1:10)] + DC10_P 

#Plots
plot(timeframe, c(P_orig[1687:1726]), 
                xlim = tfxlim, 
                ylim = c(min(c(P_orig[1637:1726],P_CI_lower)),max(c(P_orig[1687:1726],P_CI_upper))), 
                type = "l", 
                ylab= "DKK", 
                xlab = "",
                main = "Price Forecast Winter 2019-2020"
     )
legend(timeframe[1]-2.75,524,c("Real Price","CI","Forecast"), lwd=c(1,1,1), col=c("black","red","black"), lty = c("solid","dashed","dotted"), y.intersp= 0.8)
lines(c((e1-1):(e1+29)), c(P_orig[1726],P_fcst), lty = "dotted")
lines(c((e1):(e1+29)), P_CI_lower, col = "red", lty = "dashed")
lines(c((e1):(e1+29)), P_CI_upper, col = "red", lty = "dashed")
lines(c((e1-1):(e1)), c(P_orig[1726], P_CI_upper[1]), lty = "dashed", col = "red")
lines(c((e1-1):(e1)), c(P_orig[1726], P_CI_lower[1]), lty = "dashed", col = "red")
lines(timeframe, rep(0,40), col = "blue", lty = "dotted")

lines(c((e1-1):(e1+29)), c(P_orig[1726], P_actual[1:30]))
points(c((e1-1):(e1+29)), c(P_orig[1726], P_actual[1:30]))
```

Forecast Error Variance Decomposition (Not Included in Project)
```{r}
##Manual
#MSE
m <- length(Theta)
MSE <- matrix(c(0,0,0,0), 2,2)
for (i in 1:m) {
  MSE <- MSE + Theta[[i]] %*% t(Theta[[i]])
}
MSE_C <- MSE[1,1]
MSE_P <- MSE[2,2]

#FEVD
omegaC <- 0
omegaP <- 0
eC <- c(1,0); eP <- c(0,1)
for (i in 1:1) {
  omegaC <- omegaC + ((t(eC) %*% Theta[[i]] %*% eP)^2)[1]/MSE_C
  omegaP <- omegaP + ((t(eP) %*% Theta[[i]] %*% eC)^2)[1]/MSE_P
}



##Automatic
#VAR
fevd.VAR <- fevd(VAR.model)
plot(fevd.VAR)
#SVARB
fevd.SVARB <- fevd(SVARB.model, n.ahead = 10)
plot(fevd.SVARB)

```


